---
title: "An Explorotory Analysis of Young People"
author: "Ryan Pugh. Aspen Bass, Zongzhe Lin, Joseph Saah"
date: "October 17, 2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load required packages
suppressPackageStartupMessages(library(tidyverse, quietly = TRUE))
suppressPackageStartupMessages(library(lubridate, quietly = TRUE))
suppressPackageStartupMessages(library(tidyr, quietly = TRUE))
youthdata<-read_csv("responses.csv")
```

## Introduction

In 2013, students of the Statistics class at FSEV UK were asked to invite their friends to participate in this survey.

The data file (responses.csv) consists of 1010 rows and 150 columns (139 integer and 11 categorical).
For convenience, the original variable names were shortened in the data file. See the columns.csv file if you want to match the data with the original names.
The data contain missing values.
The survey was presented to participants in both electronic and written form.
The original questionnaire was in Slovak language and was later translated into English.
All participants were of Slovakian nationality, aged between 15-30.

The variables can be split into the following groups:
*Music preferences (19 items)
*Movie preferences (12 items)
*Hobbies & interests (32 items)
*Phobias (10 items)
*Health habits (3 items)
*Personality traits, views on life, & opinions (57 items)
*Spending habits (7 items)
*Demographics (10 items)

The groups relevant to our analysis are Music preferences, Movie preferences, and Demographics. This analysis is designed to show the relationship between media preferences and hand dominance, and if there are any correlations in the preferences for different media types. More specifically, the data analysis will answer the following questions:

1.  Are there differences in music preferences between left handed people and right handed people?
2.  Are there any connections between music and movie preferences?

...


## 1. Data Import and Cleaning

```{r}
youthdata2<-select(youthdata, Music:Action, Age:`Left - right handed`, -`Only child`)
youthdata2<-gather(data = youthdata2, key = "MusicGenre", value = "MusicGenreScore", Dance:Opera)
youthdata2<-gather(data = youthdata2, key = "MovieGenre", value = "MovieGenreScore", Horror:Action)
youthdata2<-select(youthdata2, MusicScore=Music, MusicGenre, MusicGenreScore, MoviesScore=Movies, MovieGenre, MovieGenreScore, Age, Height, Weight, Gender, DominateHand=`Left - right handed`)
youthdata2
```

We downloaded the data CSV and imported it into a table. The dataset had a lot of irrelevant variables to our analysis, so first we selected the relevant groups. To tidy the data, we took all the genre obserevations for Music and Movies and gathered them into the MusicGenre and MovieGenre variables respectively, with each having their values being outputted to a GenreScore. Lastly, we renamed some variables to make them more code friendly.

In are tidy dataset there are 188870 rows, and 11 columns. 7 are numerical, 4 are categorical.


## 2. Data Analysis 

May describe data tranformation you carried out before any of your analysis, and include R code.


### Question 1: Are there differences in music preferences between left handed people and right handed people?

```{r}

```

Describe data transformation specific for this question, and include R code;

Describe how you address this specific question, and include R code;

Write your answer to the quetsion based on the analysis; may look at and cite addional sources to increase your understanding about the question.


**Note: If the question contains multiple parts (small questions), you may lable them as 1a, 1b,etc. as follows:**


#### 1a: XXX

Describe data transformation specific for this question, and include R code;

Describe how you address this specific question, and include R code;

Write your answer to the quetsion based on the analysis; may look at and cite addional sources to increase your understanding about the question.


#### 1b: XXX

...


### Question 2: Are there any connections between music and movie preferences?

```{r}

```



## 3. Summary

Reflect on the exploratory analysis: 

(i)	summarize key facts learned from this analysis and discuss what you find most interesting;
(ii) may briefly discuss limitations of the analysis;
(iii)	may briefly discuss what additional data and analysis could be useful;
(iv) may discuss any other thought you have.


## References

List sources or articles you cited, if there are any.


