---
title: "An Explorotory Analysis of Young People"
author: "xxx"
date: "October 17, 2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load required packages
suppressPackageStartupMessages(library(tidyverse, quietly = TRUE))
suppressPackageStartupMessages(library(lubridate, quietly = TRUE))
suppressPackageStartupMessages(library(tidyr, quietly = TRUE))
youthdata<-read_csv("responses.csv")
```

## Introduction

In 2013, students of the Statistics class at FSEV UK were asked to invite their friends to participate in this survey.

The data file (responses.csv) consists of 1010 rows and 150 columns (139 integer and 11 categorical).
For convenience, the original variable names were shortened in the data file. See the columns.csv file if you want to match the data with the original names.
The data contain missing values.
The survey was presented to participants in both electronic and written form.
The original questionnaire was in Slovak language and was later translated into English.
All participants were of Slovakian nationality, aged between 15-30.

The variables can be split into the following groups:
*Music preferences (19 items)
*Movie preferences (12 items)
*Hobbies & interests (32 items)
*Phobias (10 items)
*Health habits (3 items)
*Personality traits, views on life, & opinions (57 items)
*Spending habits (7 items)
*Demographics (10 items)

Write about the general purpose of this analysis, and list the questions you intend to address. For example:

This analysis is designed to show .... More specifically, the data analysis will answer the following questions:

1.  Are there differences in music preferences between left handed people and right handed people?
2.  XXX
3.  XXX

...


## 1. Data Import and Cleaning

```{r}
youthdata2<-select(youthdata, Music:Action, Age:`Left - right handed`, -`Only child`)
youthdata2<-gather(data = youthdata2, key = "MusicGenre", value = "MusicGenreScore", Dance:Opera)
youthdata2<-gather(data = youthdata2, key = "MovieGenre", value = "MovieGenreScore", Horror:Action)
youthdata2<-select(youthdata2, MusicScore=Music, MusicGenre, MusicGenreScore, MoviesScore=Movies, MovieGenre, MovieGenreScore, Age, Height, Weight, Gender, DominateHand=`Left - right handed`)
youthdata2
```

Describe how you imported the data to tidyverse, what problems you found with the data, what steps you took to clean and tidy the data. Include R code.

Give a summary report of the clean dataset: how many rows and columns, variables and their data types, the first few rows of the tipple.

## 2. Data Analysis 

May describe data tranformation you carried out before any of your analysis, and include R code.


### Question 1: Are there differences in music preferences between left handed people and right handed people?

```{r}

```

Describe data transformation specific for this question, and include R code;

Describe how you address this specific question, and include R code;

Write your answer to the quetsion based on the analysis; may look at and cite addional sources to increase your understanding about the question.


**Note: If the question contains multiple parts (small questions), you may lable them as 1a, 1b,etc. as follows:**


#### 1a: XXX

Describe data transformation specific for this question, and include R code;

Describe how you address this specific question, and include R code;

Write your answer to the quetsion based on the analysis; may look at and cite addional sources to increase your understanding about the question.


#### 1b: XXX

...


### Question 2: Are there any connections between music and movie preferences?

```{r}

```



## 3. Summary

Reflect on the exploratory analysis: 

(i)	summarize key facts learned from this analysis and discuss what you find most interesting;
(ii) may briefly discuss limitations of the analysis;
(iii)	may briefly discuss what additional data and analysis could be useful;
(iv) may discuss any other thought you have.


## References

List sources or articles you cited, if there are any.


