---
title: "Midterm Project"
author: "Ryan Pugh"
date: "October 12, 2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load required packages
suppressPackageStartupMessages(library(tidyverse, quietly = TRUE))
suppressPackageStartupMessages(library(lubridate, quietly = TRUE))
suppressPackageStartupMessages(library(tidyr, quietly = TRUE))
youthdata<-read_csv("responses.csv")
```

1. At least do two sets of exploratory analyses (ask two questions) that look at: 
   * variations among observations
   * covariations between variables 
2. At least include three graphics;
3. Involve some data cleaning and data transformation;
4. Try to seek in-depth understanding

##Data Set: Young People
Variables to select: Music preferences, Movie preferences, Demographics
https://www.kaggle.com/miroslavsabo/young-people-survey

####Data Transformation:

```{r}
youthdata2<-select(youthdata, Music:Action, Age:`Left - right handed`, -`Only child`)
youthdata2<-gather(data = youthdata2, key = "MusicGenre", value = "MusicGenreScore", Dance:Opera)
youthdata2<-gather(data = youthdata2, key = "MovieGenre", value = "MovieGenreScore", Horror:Action)
youthdata2<-select(youthdata2, MusicScore=Music, MusicGenre, MusicGenreScore, MoviesScore=Movies, MovieGenre, MovieGenreScore, Age, Height, Weight, Gender, DominateHand=`Left - right handed`)
youthdata2
```

##Question 1

Are there differences in music preferences between left handed people and right handed people?

```{r}

```

##Question 2

Are there any connections between music and movie preferences?

```{r}

```

```{r}

```